An example exploratory analysis script

### 2023-03-14 code/analysis_code/exploratory_analysis.qmd

# Pathogen Type + Etiology vs Hospitalization
ggplot(training_data_final %>% 
         group_by(Pathogen_Type, Simplified_Etiology, Hospitalizations) %>% count() %>% 
         mutate(true_hospitalization = n * Hospitalizations), aes(x = Pathogen_Type, y = true_hospitalization, group = Simplified_Etiology, fill = Simplified_Etiology)) +
  geom_col() + 
  labs(x = "Pathogen Type", y = "Hospitalizations", title = "Stacked Bar Chart of Hospitalizations by Pathogen Type and Etiology")

@@

# Locations and Hospitalizations
Location_v_Hospitalization <- ggplot(training_data_final, aes(x = Location, y = Hospitalizations)) +
  geom_col() + 
  labs(x = "Locations", y = "Hospitalizations", title = "Hospitalizations by Food Type, Excluding 'Multiple' and 'Other'")+
  coord_flip()

>>>>

# Pathogen Type + Etiology vs Hospitalization
ggplot(training_data_final %>% 
         group_by(Pathogen_Type, Simplified_Etiology, Hospitalizations) %>% count() %>% 
         mutate(true_hospitalization = n * Hospitalizations), aes(x = Pathogen_Type, y = true_hospitalization, group = Simplified_Etiology, fill = Simplified_Etiology)) +
  geom_col() + 
  labs(x = "Pathogen Type", y = "Hospitalizations", title = "Stacked Bar Chart of Hospitalizations by \nPathogen Type and Etiology")

@@

# Locations and Hospitalizations
Location_v_Hospitalization <- ggplot(training_data_final, aes(x = Location, y = Hospitalizations)) +
  geom_col() + 
  labs(x = "Locations", y = "Hospitalizations", title = "Hospitalizations by Food Type, Excluding 'Multiple' and \n'Other'")+
  coord_flip()
